---
title: "example_102.Rmd"
output: html_document
---

```{r setup, include=FALSE}
library(reticulate)
```

```{r include = TRUE}
# Import Python modules
COVID19 <- import("COVID19")
Model <-COVID19$model$Model
Parameters <-COVID19$model$Parameters
simulation <- COVID19$simulation
```

```{r include = TRUE}
# Parameter input arguments
input_parameter_file <- "../tests/data/baseline_parameters.csv"
parameter_line_number <- 1
output_dir <- "."
household_demographics_file <- "../tests/data/baseline_household_demographics.csv"
hospital_file <- "../tests/data/hospital_baseline_parameters.csv"
```


```{r include = TRUE}
# Instantiate Parameters object, Model object, and Simulation object
params <- Parameters(
    input_parameter_file, 
    parameter_line_number,
    output_dir,
    household_demographics_file, 
    hospital_file)

# Set end time of the simulation
params$set_param( "n_total", 50000 )
params$set_param( "end_time", 500 )

model <- simulation$COVID19IBM(model = Model(params))
sim <- simulation$Simulation(env = model, end_time = params$get_param("end_time"))
```

Run the model until there are 500 infecteds

```{r include = TRUE}
sim$steps(1L)
while( sim$results$total_infected[length(sim$results$total_infected)] < 500){
    sim$steps(1L) # needs to be an integer
}
```

Turn on lockdown and run the model for another 30 days

```{r include = TRUE}
sim$env$model$update_running_params("lockdown_on", 1)
sim$steps(30L)
```

Now turn off the lockdown and turn on digital contract tracing, with the following options.

1. 80% of people self-quarantine along with their household when they develop symptoms.
2. Tracing happens as soon as somebody develops symptoms and contacts quarantine themselves.
3. The households members of those traced also quarantine

We then run the simulation for another 100 days.
    
```{r, include = TRUE}
sim$env$model$update_running_params("lockdown_on", 0)

# 80% self-quarantine along with their households
sim$env$model$update_running_params("self_quarantine_fraction", 0.8 )
sim$env$model$update_running_params("quarantine_household_on_symptoms", 1 )

# turn on the app and quarantine those people who have been traced along with their households
sim$env$model$update_running_params("app_turned_on", 1 )
sim$env$model$update_running_params("quarantine_on_traced", 1 )
sim$env$model$update_running_params("trace_on_symptoms", 1 )
sim$env$model$update_running_params("quarantine_household_on_traced_symptoms", 1 )

# step forwrard another 100 days
sim$steps( 100L )
```

Plot total infected through time

```{r, include = TRUE}
plot(sim$results$time, sim$results$total_infected, 
     type = "l", col = "blue", xlab = "Time", ylab = "Total infected")
```
